Pillar 1 - Sequential Pattern Mining

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
debug cspade

The parameter values are: 
support:  a numeric value specifying the minimum support of a sequence (default 0.1, range [0,1]).
maxsize:  an integer value specifying the maximum number of items of an element of a sequence (default 10, range > 0).
maxlen:   an integer value specifying the maximum number of elements of a sequence (default 10, range > 0).
mingap:   an integer value specifying the minimum time difference between consecutive elements of a sequence (default none, range >= 1).
maxgap:   an integer value specifying the maximum time difference between consecutive elements of a sequence (default none, range >= 0).
maxwin:   an integer value specifying the maximum time difference between any two elements of a sequence (default none, range >= 0).

##Creating look-up table
```{r}
lookup_table <- d_course %>%

  select(`Student ID`, #Item, 
         `Course ID`, !!category, Time) %>% # Course ID and Time may not be necessary

###NOTE for FURTURE: create filter by function
##Create filter condition.
```{r}
string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
                           quo_name(category)=="Low_grade"      ~ "low score",
                           quo_name(category)=="Discrete_grade" ~ "5",
                           quo_name(category)=="None"           ~ "_" #useless filter
                           )
```
##CSPADE Algorithm:
```{r}
frequent_trajectories <- cspade(transactions, parameter = list(support = 0,
                                                               maxsize = 1,
                                                               maxlen = 2), control   = list(verbose = TRUE))

@@

  # Compute statistics
  group_by(LHS,`RHS Course ID`) %>%
  arrange(LHS,`RHS Course ID`)
  mutate(
    Prob_both = sum(support), 
    Conf_corr = support/Prob_both,
    n_rule    = support * n_students,
    n_both    = Prob_both * n_students,
    lift_diff = Conf_corr - Prop_low,
    lift_corr = Conf_corr / Prop_low
    ) %>%
  ungroup() %>%

>>>>

```{r}
subsequences <- sequences %>%
  cspade(
    parameter = list(
      support = 0, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4, # max time difference between consecutive element of a sequence
      maxwin  = 1e4  # max time difference between any two elements of a sequence
      ),
    control = list(
      verbose = FALSE
      )
    )

#Inspect results CSPADE
summary(subsequences)
as(subsequences, "data.frame")
```

##rule induction:
```{r}
rules <- ruleInduction(frequent_trajectories,
                       confidence = 0, #we need to play with the parameters.
                       control    = list(verbose = TRUE))

@@

  # Compute statistics
  group_by(LHS,`RHS Course ID`) %>%
  arrange(LHS,`RHS Course ID`) %>%
  mutate(
    Prob_both = sum(support), 
    Conf_corr = support/Prob_both,
    n_rule    = support * n_students,
    n_both    = Prob_both * n_students,
    lift_diff = Conf_corr - Prop_low,
    lift_corr = Conf_corr / Prop_low
    ) %>%
  ungroup() %>%
